---
title: "Inclass Assignment (1)"
author: "Akshar Patel"
date: "1/19/2022"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

# Inclass Assignment (1) - closed book unless specified

### To answer a question, remove `#YOUR CODE HERE` and #`YOUR ANSWER HERE`, and then write down your code and/or answer.

### Q1. Replace `author name` with your name (line 3) and `date` with today's date (line 4) above.   

### Q2. Install `ggplot2` package (remove #YOUR CODE HERE comment and then write down your code)
```{r, echo=TRUE, error = TRUE, eval = FALSE}
install.packages("ggplot2")
```

### Q3. Load `ggplot2` package
```{r}
library(ggplot2) 
```

### Q4. You want to store a value 3.45 into the variable `float_new_project` as follows. Answer 1) whether the following code is correct or incorrect. 2) If incorrect, why? (0.5 point, respectively)
```{r}
float_new_project -> 3.45 
# 1) Incorrect
float_new_project <- 3.45
```

### Q5. You want to store a value `financial report` into the variable `2021 annual report` as follows. Answer 1) whether the following code is correct or incorrect. 2) If incorrect, why? (0.5 point, respectively)
```{r}
2021 annual report <- "financial report" 
# 1) InCorrect

```

### Q6. Store five values `43, 21, 34, 19, 62` into the `ages` variable using `c()`
### Assignment - multiple values (vector)
```{r}
ages <- c(43, 21, 34, 19, 62)
```

### Q7. Write a code that finds the minimun value of `ages` that you have created in Q6
```{r}
min(ages)
```

### Q8. Assign the value of 3 raised to 3 to a variable `generation`. Then, print out the value of `generation`.
```{r}
generation <- 3^3
print(generation)
```

### Q9. 1) Assign the value of square root 144 to a variable `tree`. Then, 2) print out `tree`. (0.5 point, respectively)
```{r}
tree <- sqrt(144)
print(tree)
```

### Q10. You want to store a text `mozart` into the variable `piano` as follows. Answer 1) whether the following code is correct or incorrect. 2) If incorrect, why? (0.5 point, respectively)
```{r}
piano <- mozart 
# 1) Incorrect
# 2)  the correct way would be piano <- "mozart"
```

### *End of document*
